---
title: "hmk6"
author: "Xinyi Wang"
date: "12/7/2020"
output: github_document
---


```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


```{r load_libraries}
library(tidyverse)
library(modelr)
library(p8105.datasets)
```

### Problem 1

```{r}
homicide_df = 
  read_csv("homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```


Start with one city.

```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")
glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```


Try this across cities.

```{r}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI")) 
```

```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```



## Problem 2

###load data

```{r}
baby_df = 
  read_csv("birthweight.csv") 
```

### clean the data for regression 

There is no missing data.

```{r}
baby_df = 
 baby_df %>% 
 mutate(
  babysex = factor(case_when(
   babysex == 1 ~ "male",
   babysex == 2 ~ "female"
   )),
  frace = factor(case_when(
   frace == 1 ~ "white",
   frace == 2 ~ "black",
   frace == 3 ~ "asion",
   frace == 4 ~ "puerto",
   frace == 8 ~ "other",
   frace == 9 ~ "unknown")),
  malform = factor(case_when(
   malform == 0 ~ "absent",
   malform == 1 ~ "present"
  )),
  mrace = factor(case_when(
   mrace == 1 ~ "white",
   mrace == 2 ~ "black",
   mrace == 3 ~ "asion",
   mrace == 4 ~ "puerto",
   mrace == 8 ~ "other")),
  
# turn grams into pounds
  bwt = bwt *0.00220462262185
 ) 
 

sum(is.na(baby_df))
```


### take a look at variables

Finally choose 7 parameters with p-value < 0.05. They are babysex, bhead, blength, delwt, gaweeks, parity, smoken. 

```{r}

baby_df %>% 
 lm(bwt ~ ., data = .) %>% 
 broom::tidy() %>% 
 filter (p.value < 0.05 ) %>% 
 knitr::kable()
  
```

### look at the model with filtered parameter 

```{r}
my_model = lm(bwt ~ babysex + bhead + blength + delwt + gaweeks + parity + smoken, data = baby_df) 


my_model %>% 
 broom::tidy() %>% 
 select(term, estimate, p.value)
```

```{r}
baby_df %>%
  modelr::add_residuals(my_model) %>% 
  modelr::add_predictions(my_model)%>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point(alpha = 0.3) +
  geom_smooth(method = "lm", color = "red", linetype = 2) +
  labs(title = "plot of Predictions and Residuals(pounds)", 
       x = "Predictions ", 
       y = "Residuals")

```

From the plot, we can see that all points are gathered together. There is no significant relationship between them.

### Compare models to two others


```{r}
model_1 = lm(bwt ~ blength + gaweeks, data = baby_df)
model_1 %>% 
 broom::tidy() %>% 
 select(term, estimate, p.value)

model_2 = lm(bwt ~ bhead * blength * babysex, data = baby_df)
model_2 %>% 
 broom::tidy() %>% 
 select(term, estimate, p.value)
```

### compare with cross validation

```{r}
cv_df =
  crossv_mc(baby_df, 200) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))

cv_df = 
  cv_df %>% 
  mutate(
    my_model  = map(train, ~lm(bwt ~ babysex + bhead + blength + delwt + gaweeks + parity + smoken, data = baby_df)),
    model_1  = map(train, ~lm(bwt ~ blength + gaweeks, data = baby_df)),
    model_2  = map(train, ~lm(bwt ~ bhead * blength * babysex, data = baby_df))) %>% 
  mutate(
    rmse_my = map2_dbl(my_model, test, ~rmse(model = .x, data = .y)),
    rmse_1 = map2_dbl(model_1, test, ~rmse(model = .x, data = .y)),
    rmse_2 = map2_dbl(model_2, test, ~rmse(model = .x, data = .y)))
```

### make a plot to see the comparison

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin() +
  labs( 
   title = "Compare three models with cross validtion")
```

We could find out that my_model has lowest rmse, which means that it could be the best model among these three models, and the model using length at birth and gestational age as prediction has the highest rmse and performs worst. 


## Problem 3

### load data

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


```{r}
boot_straps = 
  weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::tidy),
    glance = map(models, broom::glance)) %>%
  unnest(results, glance) %>% 
  select(.id, term, estimate, r.squared)

```

### calculate log_beta and r.square

```{r}
boot_straps = 
 boot_straps %>% 
 pivot_wider(
    names_from = term,
    values_from = estimate) %>% 
  rename(
    beta_0 = `(Intercept)`,
    beta_1 = tmin) %>% 
  mutate(log_beta = log(beta_0*beta_1)) %>% 
  select(r.squared, log_beta)
```


### Plot distribution of my estimate

```{r}
boot_straps %>% 
 ggplot(aes(x = log_beta)) +
 geom_density() +
 labs(
  title = "Distribution of log beta",
  x = "log beta",
  y= "Density"
 )


boot_straps %>% 
 ggplot(aes(x = r.squared)) +
 geom_density() +
 labs(
  title = "Distribution of r square",
  x = "r square",
  y= "Density"
 )
```

We could find that both log_beta and r square are nearly normal distribution. And r square is quite large, which indicates that tim and tmax are relative to some extent.


### confidence intercal for r square and log beta

```{r}
boot_straps %>% 
  summarize(
    estimate = c("r square", "log beta"),
    ci_lower = c(quantile(r.squared, 0.025), quantile(log_beta, 0.025)),
    ci_upper = c(quantile(r.squared, 0.975), quantile(log_beta, 0.975))) %>% 
  knitr::kable()
```

