---
title: "hmk6"
author: "Xinyi Wang"
date: "12/7/2020"
output: github_document
---


```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


```{r load_libraries}
library(tidyverse)
library(modelr)
library(p8105.datasets)
```

### Problem 1

```{r}
homicide_df = 
  read_csv("homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```


Start with one city.

```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")
glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```


Try this across cities.

```{r}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI")) 
```

```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```



## Problem 2

load data

```{r}
baby_df = 
  read_csv("birthweight.csv") 
```

clean the data for regression 

There is no missing data

```{r}
baby_df = 
 baby_df %>% 
 mutate(
  babysex = factor(case_when(
   babysex == 1 ~ "male",
   babysex == 2 ~ "female"
   )),
  frace = factor(case_when(
   frace == 1 ~ "white",
   frace == 2 ~ "black",
   frace == 3 ~ "asion",
   frace == 4 ~ "puerto",
   frace == 8 ~ "other",
   frace == 9 ~ "unknown")),
  malform = factor(case_when(
   malform == 0 ~ "absent",
   malform == 1 ~ "present"
  )),
  mrace = factor(case_when(
   mrace == 1 ~ "white",
   mrace == 2 ~ "black",
   mrace == 3 ~ "asion",
   mrace == 4 ~ "puerto",
   mrace == 8 ~ "other")),
  
  bwt = bwt *0.00220462262185
 ) 
 

sum(is.na(baby_df))
```


take a look at variables and finally choose 7 parameters with p-value < 0.05. They are babysex, bhead, blength, delwt, gaweeks, parity, smoken. 

```{r}

baby_df %>% 
 lm(bwt ~ ., data = .) %>% 
 broom::tidy() %>% 
 filter (p.value < 0.05 ) %>% 
 knitr::kable()
  
```

change the benchmark and look at the model with filtered parameter 

```{r}
model = baby_df %>% 
 mutate(babysex = fct_infreq(babysex)) %>% 
 lm(bwt ~ babysex + bhead + blength + delwt + gaweeks + parity + smoken, data = .) %>% 
 broom::tidy() %>% 
 select(term, estimate, p.value)
```

```{r eval=FALSE, include=FALSE}
baby_df %>%
  modelr::add_residuals(model) %>% 
  modelr::add_prediction(model) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point()
```